Discrete Quantum Theories and Computing

### 2018-04-05 dissertation.tex
CV_thesis.pdf Updating...

\maketitle
%data for Acceptance Page
\committeeMember{Amr A. Sabry, PhD} \committeeMember{Gerardo
Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
Date} \acceptancepage

@@

\begin{dedication}I would like to dedicate my thesis to my parents,
Cheng-Tien Tai and Feng-Ming Chang. Thank for your support during
my Ph.D. study. \end{dedication}

@@

Thank Elizabeth ``Betsy'' Merceron and Kexin Chen for helping me
pass TEPAIC exam. \end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}

>>>>

\maketitle
%data for Acceptance Page
\committeeMember{Amr A. Sabry , PhD} \committeeMember{Gerardo
Ortiz, PhD} \committeeMember{Dylan Paul Thurston, PhD} \committeeMember{Andrew
J. Hanson, PhD} \committeeMember{Shouhong Wang, PhD} \defensedate{Defense
Date} \acceptancepage

@@

\begin{dedication}I would like to dedicate my thesis to my parents,
Cheng-Tien Tai  and Feng-Ming Chang. Thanks for encouraging me to
study abroad and all your support during my Ph.D. study. \end{dedication}

@@

Thank Elizabeth ``Betsy'' Merceron and Kexin Chen for helping me
pass TEPAIC exam.

Finally, thank Jin-Ru Yang for handling my hand and leading me here,
and hope I could be with you to wherever place until the death separating
us apart eventually.\end{acknowledgments}
\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.
\end{abstract}
\tableofcontents{}
